Biodegradable alternatives to plastic mesh bags conventionally used in freshwater

### 2023-08-09 Rdocs/ManuscriptLPP.Rmd
cleaned up comments added scaling to PCA analysis
added PCA corrplot to ManuscriptLPP.Rmd

#PCA plot:----
#dotplot between pc1 and pc2, with % explained variance annotated in axis labels
ggplot(data = LPP_FullData, aes(x = PC1, y = PC2, fill = material)) +
  geom_point(shape = 21, size = 2.5) + 
geom_abline(slope = 0, intercept = 0, linetype = 2) +
  geom_vline(xintercept = 0, linetype = 2) +

>>>>

#PCA plot:----
#prin comp correl plot for all components
corrplot(taxaCount_PCA$rotation)

#dotplot between pc1 and pc2, with % explained variance annotated in axis labels
ggplot(data = LPP_FullData, aes(x = PC1, y = PC2, fill = material)) +
  geom_point(shape = 21, size = 2.5) + 
geom_abline(slope = 0, intercept = 0, linetype = 2) +
  geom_vline(xintercept = 0, linetype = 2) +
